Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the \texttt{eechidna} \texttt{R} package.

### 2019-03-31 draft-paper.tex
updated first draft

\emph{1: HERE Introductory paragraph}
Electoral socio-demographic variables are now available for each of the six elections and are joined with their corresponding two-party preferred votes. Before choosing an appropriate model, two issues with the socio-demographic variables are addressed. Firstly, variable scales change over the years, making it important to standardize variables. Secondly, many variables represent similar information and where appropriate, should be combined in some way. Principal component analysis is used to identify variables covary, from which intuitive groupings are selected to be combined into a single variable. This also reduces the dimension of the data. After these steps, a model specification is chosen.

@@

\emph{2: HERE - ADD JUSTIFICATION FOR DOING SINGLE PCA AND EXPLAIN FACTORS CREATED}

@@

{\centering \includegraphics[width=0.8\linewidth,]{draft-paper_files/figure-latex/resstate-1}

@@

\emph{3: HERE Add paragraph on the overall strategy and contributions - can restate stuff from intro}

@@

\caption{Partial residual plots for: income and unemployment, industry and type of work, and household mobility.}\label{fig:partresplot1}
\end{figure}

@@

\caption{Partial residual plots for: relationships and age, education and diversity.}\label{fig:partresplot2}
\end{figure}

>>>>

Electoral socio-demographic variables are now available for each of the six elections and are joined with their corresponding two-party preferred votes. Before choosing an appropriate model, two issues with the socio-demographic variables are addressed. Firstly, variable scales change over the years, making it important to standardize variables. Secondly, many variables represent similar information and where appropriate, should be combined in some way. Principal component analysis is used to identify variables covary, from which intuitive groupings are selected to be combined into a single variable. This also reduces the dimension of the data. After these steps, a model specification is chosen.

@@

@@

{\centering \includegraphics[width=0.7\linewidth,]{draft-paper_files/figure-latex/resstate-1}

@@

@@

\caption{Partial residual plots for: Incomes, Unemployment, Extractive, Transformative, ManagerAdmin and DiffAddress}\label{fig:partresplot1}
\end{figure}

@@

\caption{Partial residual plots for: DeFacto, MedianAge, Education, OtherLanguage, BornSEEuro, BornAsia and Judaism.}\label{fig:partresplot2}
\end{figure}
